---
title: "Introduction to Data Science"
subtitle: "Homework 1"
author: "Miguel Amaral - `mamaral7542@floridapoly.edu`"
output: html_notebook
---



# Problem 1 

|Class Name    |   Prefix      |    Number     |         Credits
|-----------    |  ---------    | -----------   |   --------
|_Introduction to Data Science_|**COP**|**2073**|3|
|_Introduction to Business Finance_|**FIN**|**2001**|3|
|_Legal, Ethical, and Management_|**IDS**|**2144**|3|
|_Law, Public Policy, and Negotiation in Business_|**BUL**|**2241**|3|
|_International & Comparative Dimensions of Business_|**GEB**|**3343**|3|

# Problem 2



## Introduction to Finance

- **Gross Capital Formation** is the amount of outlays on additions to the fixed assets of the economy plus net change in inventories.
- **Gross domestic product** (GDP) is a measure of the nation’s output of goods and services for a specified period of time. Increases in GDP over time measure the extent of economic growth, one of the nation’s long term economic policy objectives.
- **Financial assets** include money, debt securities, financial contracts and equity securities that are backed by real assets and/or the earning power of the issuers

Sources: [Investopedia](https://www.investopedia.com/terms/c/capital-formation.asp)



## International & Comparative Dimensions

- **Nationalization** refers to when a government takes control of a company or industry, which generally occurs without compensation for the loss of the net worth of seized assets and potential income. 
- **Expropriation** is the act of a government taking privately owned property against the wishes of the owners, ostensibly to be used for the benefit the overall public. 
- **Confiscation** is a legal form of seizure by a government or other public authority. The word is also used, popularly, of spoliation under legal forms, or of any seizure of property as punishment or in enforcement of the law.

Sources: [Investopedia](https://www.investopedia.com/)


# Problem 3

(a) Create a variable called `my_name` that contains your preferred name.
```{r}
my_name <- "Miguel"
```


(b) Create a variable called `name_length` that holds how many letters are in `my_name`.
```{r}
name_length <- nchar(my_name)
```


(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 

```{r}
variable1 <- exp(1)^pi
variable2 <- pi^exp(1)

print(variable1)
print(variable2)

max(variable1,variable2)


```
Variable 1 e^pi is bigger.

(d) Define a function called `add_tree` that takes a single argument and returns a value 3 times larger than the input.
```{r}
add_tree <- function(argument){
  argument*3
}
print(argument)
```


(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.

```{r}
v <- 10:49
length(v)
print(v)
```


(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.
```{r}
range_of_numbers <- seq(-5,10,0.5) 
print(range_of_numbers)
```
 


